Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-02-12 main.tex

The primary contribution of this manuscript is the derivation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., $n=2$ or $n=3$).
However, we believe there are ample opportunities for refining our estimates of Poincar\'e--Friedrichs constants and extending the technique to further applications.

>>>>

The primary contribution of this manuscript is the derivation of upper bounds of Poincar\'e--Friedrichs constants for the curl and divergence operators over local patches in low dimensions (i.e., $n=2$ or $n=3$).
However, we believe there are ample opportunities for refining our estimates of Poincar\'e--Friedrichs constants, both conceptually and algorithmically, and extending the technique to further applications.
